---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(hitchr)
random_sample <- h2g2(10)
```

<!-- README.md is generated by README.Rmd. Please edit .Rmd file. -->

# hitchr
Random sample generator inspired by Douglas Adams' The Hitchhiker's Guide to the Galaxy

<!-- badges: start -->
[![build status](https://github.com/bbartholdy/hitchr/workflows/R-CMD-check/badge.svg)](https://github.com/bbartholdy/hitchr/actions)
[![Codecov test coverage](https://codecov.io/gh/bbartholdy/hitchr/branch/master/graph/badge.svg)](https://codecov.io/gh/bbartholdy/hitchr?branch=master)
<!-- badges: end -->

Currently in development.

To install:

```{r eval=FALSE}
remotes::install_github("bbartholdy/hitchr")
```

:exclamation:**Important Note**:exclamation:

This package deals with the concept of 'race' in a strictly biological sense;
i.e., there is no way to biologically distinguish discrete races within the 
*Homo sapiens* species (despite claims to the contrary).

This should not distract from the very real concept of social 'race', and the social
injustice that currently persists across the globe.

[BlackLivesMatter](https://blacklivesmatter.com/)

[StopAsianHate](https://www.stopasianhate.info/)

## Examples

```{r eval=FALSE}
hitchr::h2g2(10) # generates a random sample of 10 individuals
```

```{r echo=FALSE}
knitr::kable(random_sample)
```

Races currently available:

```{r}
hitchr:::race_index()
```

Stats currently available:

```{r}
hitchr:::stats_index()
```



